---
title: "AlberdiLab | "
subtitle: "Study title to be added"
author:
  - 
date: "Last update: `r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
url: https://alberdilab.github.io/calotriton_respirometry
description: |
  Data analysis code for the study on the recovery of metagenome‑assembled genomes and derived microbial communities from lizard faecal samples.
link-citations: yes
github-repo: alberdilab/calotriton_respirometry
---

```{r knitr_opts, echo=FALSE}
knitr::opts_chunk$set(
    class.source = "script-source",
    class.output = "script-output",
    comment = NA)
```

# Introduction

This webbook contains all the code used for data analysis in study of the individual-level metagenomic data of Podarcis muralis and Podarcis liolepis lizards from different environments during an experimental setup.

## Prepare the R environment

### Environment

To reproduce all the analyses locally, clone this repository in your computer using:

```
RStudio > New Project > Version Control > Git
```

And indicating the following git repository:

> https://github.com/alberdilab/calotriton_respirometry.git

Once the R project has been created, follow the instructions and code chunks shown in this webbook.

### Libraries

The following R packages are required for the data analysis.

```{r load_libraries, warning=FALSE, comments="", message=FALSE}
# Base
library(R.utils)
library(knitr)
library(tidyverse)
library(devtools)
library(tinytable)
library(readxl)
library(readr)
library(hms)
library(dplyr)

# For respirometry data
library(respR)

# For plotting
library(ggplot2)
library(ggpmisc)
library(ggpubr)

# For statistics
library(nlme)
library(lme4)
library(rstatix)

```
