# Data input and cleaning

```{r data_input, include=FALSE, eval=FALSE}
Harpea1_acclimatacion<-read_table('data/2023-08-17_094925_Harpea1_acclimatacion.txt')
Goizueta5_acclimatacion<-read_table("data/2023-08-17_101605_Goizueta5_acclimatacion.txt")
Erlan8_acclimatacion<-read_table('data/2023-08-17_103916_Erlan8_acclimatacion.txt')
Leitzaran7_acclimatacion<-read_table('data/2023-08-17_110619_Leitzaran7_acclimatacion.txt')
Harpea5_acclimatacion<-read_table('data/2023-08-17_113404_Harpea5_acclimatacion.txt')
Goizueta7_acclimatacion<-read_table('data/2023-08-17_120343_Goizueta7_acclimatacion.txt')
Leitzaran3_acclimatacion<-read_table('data/2023-08-17_122902_Leitzaran3_acclimatacion.txt')
Erlan3_acclimatacion<-read_table('data/2023-08-17_125030_Erlan3_acclimatacion.txt')
Goizueta1_post1<-read_table('data/2023-08-21_094955_Goizueta1_post1.txt')
Leitzaran7_post1<-read_table('data/2023-08-21_101049_Leitzaran7_post1.txt')
Erlan7_post1<-read_table('data/2023-08-21_103126_Erlan7_post1.txt')
Leitzaran6_post1<-read_table('data/2023-08-21_105116_Leitzaran6_post1.txt')
Goizueta3_post1<-read_table('data/2023-08-21_111049_Goizueta3_post1.txt')
Harpea1_post1<-read_table('data/2023-08-21_113410_Harpea1_post1.txt')
Erlan5_post1<-read_table('data/2023-08-21_115523_Erlan5_post1.txt')
Goizueta5_post1<-read_table('data/2023-08-21_121632_Goizueta5_post1.txt')
Erlan4_post1<-read_table('data/2023-08-21_123905_Erlan4_post1.txt')
Harpea8_post1<-read_table('data/2023-08-21_130550_Harpea8_post1.txt')
Goizueta8_post1<-read_table('data/2023-08-21_132625_Goizueta8_post1.txt')
Erlan3_post1<-read_table('data/2023-08-21_134514_Erlan3_post1.txt')
Erlan2_post1<-read_table('data/2023-08-21_140632_Erlan2_post1.txt')
Harpea6_post1<-read_table('data/2023-08-21_142652_Harpea6_post1.txt')
Leitzaran3_post1<-read_table('data/2023-08-21_144708_Leitzaran3_post1.txt')
Leitzaran4_post1<-read_table('data/2023-08-21_150820_Leitzaran4_post1.txt')
Harpea3_post1<-read_table('data/2023-08-22_094417_Harpea3_post1.txt')
Goizueta2_post1<-read_table('data/2023-08-22_101033_Goizueta2_post1.txt')
Harpea2_post1<-read_table('data/2023-08-22_103515_Harpea2_post1.txt')
Goizueta9_post1<-read_table('data/2023-08-22_105835_Goizueta9_post1.txt')
Leitzaran5_post1<-read_table('data/2023-08-22_112008_Leitzaran5_post1.txt')
Erlan8_post1<-read_table('data/2023-08-22_114405_Erlan8_post1.txt')
Erlan6_post1<-read_table('data/2023-08-22_121045_Erlan6_post1.txt')
Goizueta3_post1<-read_table('data/2023-08-22_123044_Goizueta3_post1.txt')
Goizueta4_post1<-read_table('data/2023-08-22_125531_Goizueta4_post1.txt')
Leitzaran2_post1<-read_table('data/2023-08-22_131557_Leitzaran2_post1.txt')
Leitzaran1_post1<-read_table('data/2023-08-22_134014_Leitzaran1_post1.txt')
Harpea5_post1<-read_table('data/2023-08-22_140250_Harpea5_post1.txt')
Goizueta7_post1<-read_table('data/2023-08-22_142225_Goizueta7_post1.txt')
Goizueta6_post1<-read_table('data/2023-08-22_144247_Goizueta6_post1.txt')
Harpea7_post1<-read_table('data/2023-08-22_150338_Harpea7_post1.txt')
Erlan1_post1<-read_table('data/2023-08-22_152239_Erlan1_post1.txt')
Goizueta3_post2<-read_table('data/2023-08-31_094117_Goizueta3_post2.txt')
Goizueta9_post2<-read_table('data/2023-08-31_100528_Goizueta9_post2.txt')
Goizueta1_post2<-read_table('data/2023-08-31_102820_Goizueta1_post2.txt')
Erlan6_post2<-read_table('data/2023-08-31_104927_Erlan6_post2.txt')
Leitzaran6_post2<-read_table('data/2023-08-31_111442_Leitzaran6_post2.txt')
Erlan5_post2<-read_table('data/2023-08-31_113759_Erlan5_post2.txt')
Erlan7_post2<-read_table('data/2023-08-31_120144_Erlan7_post2.txt')
Leitzaran3_post2<-read_table('data/2023-08-31_123046_Leitzaran3_post2.txt')
Erlan3_post2<-read_table('data/2023-08-31_125140_Erlan3_post2.txt')
Erlan2_post2<-read_table('data/2023-08-31_131345_Erlan2_post2.txt')
Erlan1_post2<-read_table('data/2023-08-31_133612_Erlan1_post2.txt')
Erlan4_post2<-read_table('data/2023-08-31_140114_Erlan4_post2.txt')
Goizueta8_post2<-read_table('data/2023-08-31_142504_Goizueta8_post2.txt')
Harpea8_post2<-read_table('data/2023-08-31_144722_Harpea8_post2.txt')
Leitzaran1_post2<-read_table('data/2023-08-31_151009_Leitzaran1_post2.txt')
Harpea6_post2<-read_table('data/2023-09-01_093457_Harpea6_post2.txt')
Leitzaran2_post2<-read_table('data/2023-09-01_095525_Leitzaran2_post2.txt')
Goizueta4_post2<-read_table('data/2023-09-01_103810_Goizueta4_post2.txt')
Leitzaran4_post2<-read_table('data/2023-09-01_110108_Leitzaran4_post2.txt')
Harpea7_post2<-read_table('data/2023-09-01_112139_Harpea7_post2.txt')
Harpea5_post2<-read_table('data/2023-09-01_114208_Harpea5_post2.txt')
Goizueta6_post2<-read_table('data/2023-09-01_121221_Goizueta6_post2.txt')
Goizueta7_post2<-read_table('data/2023-09-01_123729_Goizueta7_post2.txt')
Leitzaran7_post2<-read_table('data/2023-09-01_130235_Leitzaran7_post2.txt')
Leitzaran5_post2<-read_table('data/2023-09-01_132508_Leitzaran5_post2.txt')
Goizueta2_post2<-read_table('data/2023-09-01_134650_Goizueta2_post2.txt')
Erlan8_post2<-read_table('data/2023-09-02_092910_Erlan8_post2.txt')
Goizueta5_post2<-read_table('data/2023-09-02_095527_Goizueta5_post2.txt')
Harpea1_post2<-read_table('data/2023-09-02_101555_Harpea1_post2.txt')
Harpea2_post2<-read_table('data/2023-09-02_103821_Harpea2_post2.txt')
Harpea3_post2<-read_table('data/2023-09-02_105923_Harpea3_post2.txt')
```

```{r data_modify, include=FALSE, eval=FALSE}
colnames(Harpea1_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Harpea1_acclimatacion))
colnames(Goizueta5_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Goizueta5_acclimatacion))
colnames(Erlan8_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Erlan8_acclimatacion))
colnames(Leitzaran7_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Leitzaran7_acclimatacion))
colnames(Harpea5_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Harpea5_acclimatacion))
colnames(Goizueta7_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Goizueta7_acclimatacion))
colnames(Leitzaran3_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Leitzaran3_acclimatacion))
colnames(Erlan3_acclimatacion)<-gsub("\\[|\\]", "_", colnames(Erlan3_acclimatacion))
colnames(Goizueta1_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta1_post1))
colnames(Leitzaran7_post1)<-gsub("\\[|\\]", "_", colnames(Leitzaran7_post1))
colnames(Erlan7_post1)<-gsub("\\[|\\]", "_", colnames(Erlan7_post1))
colnames(Leitzaran6_post1)<-gsub("\\[|\\]", "_", colnames(Leitzaran6_post1))
colnames(Goizueta3_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta3_post1))
colnames(Harpea1_post1)<-gsub("\\[|\\]", "_", colnames(Harpea1_post1))
colnames(Erlan5_post1)<-gsub("\\[|\\]", "_", colnames(Erlan5_post1))
colnames(Goizueta5_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta5_post1))
colnames(Erlan4_post1)<-gsub("\\[|\\]", "_", colnames(Erlan4_post1))
colnames(Harpea8_post1)<-gsub("\\[|\\]", "_", colnames(Harpea8_post1))
colnames(Goizueta8_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta8_post1))
colnames(Erlan3_post1)<-gsub("\\[|\\]", "_", colnames(Erlan3_post1))
colnames(Erlan2_post1)<-gsub("\\[|\\]", "_", colnames(Erlan2_post1))
colnames(Harpea6_post1)<-gsub("\\[|\\]", "_", colnames(Harpea6_post1))
colnames(Leitzaran3_post1)<-gsub("\\[|\\]", "_", colnames(Leitzaran3_post1))
colnames(Leitzaran4_post1)<-gsub("\\[|\\]", "_", colnames(Leitzaran4_post1))
colnames(Harpea3_post1)<-gsub("\\[|\\]", "_", colnames(Harpea3_post1))
colnames(Goizueta2_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta2_post1))
colnames(Harpea2_post1)<-gsub("\\[|\\]", "_", colnames(Harpea2_post1))
colnames(Goizueta9_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta9_post1))
colnames(Leitzaran5_post1)<-gsub("\\[|\\]", "_", colnames(Leitzaran5_post1))
colnames(Erlan8_post1)<-gsub("\\[|\\]", "_", colnames(Erlan8_post1))
colnames(Erlan6_post1)<-gsub("\\[|\\]", "_", colnames(Erlan6_post1))
colnames(Goizueta3_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta3_post1))
colnames(Goizueta4_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta4_post1))
colnames(Leitzaran2_post1)<-gsub("\\[|\\]", "_", colnames(Leitzaran2_post1))
colnames(Leitzaran1_post1)<-gsub("\\[|\\]", "_", colnames(Leitzaran1_post1))
colnames(Harpea5_post1)<-gsub("\\[|\\]", "_", colnames(Harpea5_post1))
colnames(Goizueta7_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta7_post1))
colnames(Goizueta6_post1)<-gsub("\\[|\\]", "_", colnames(Goizueta6_post1))
colnames(Harpea7_post1)<-gsub("\\[|\\]", "_", colnames(Harpea7_post1))
colnames(Erlan1_post1)<-gsub("\\[|\\]", "_", colnames(Erlan1_post1))
colnames(Goizueta3_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta3_post2))
colnames(Goizueta9_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta9_post2))
colnames(Goizueta1_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta1_post2))
colnames(Erlan6_post2)<-gsub("\\[|\\]", "_", colnames(Erlan6_post2))
colnames(Leitzaran6_post2)<-gsub("\\[|\\]", "_", colnames(Leitzaran6_post2))
colnames(Erlan5_post2)<-gsub("\\[|\\]", "_", colnames(Erlan5_post2))
colnames(Erlan7_post2)<-gsub("\\[|\\]", "_", colnames(Erlan7_post2))
colnames(Leitzaran3_post2)<-gsub("\\[|\\]", "_", colnames(Leitzaran3_post2))
colnames(Erlan3_post2)<-gsub("\\[|\\]", "_", colnames(Erlan3_post2))
colnames(Erlan2_post2)<-gsub("\\[|\\]", "_", colnames(Erlan2_post2))
colnames(Erlan1_post2)<-gsub("\\[|\\]", "_", colnames(Erlan1_post2))
colnames(Erlan4_post2)<-gsub("\\[|\\]", "_", colnames(Erlan4_post2))
colnames(Goizueta8_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta8_post2))
colnames(Harpea8_post2)<-gsub("\\[|\\]", "_", colnames(Harpea8_post2))
colnames(Leitzaran1_post2)<-gsub("\\[|\\]", "_", colnames(Leitzaran1_post2))
colnames(Harpea6_post2)<-gsub("\\[|\\]", "_", colnames(Harpea6_post2))
colnames(Leitzaran2_post2)<-gsub("\\[|\\]", "_", colnames(Leitzaran2_post2))
colnames(Goizueta4_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta4_post2))
colnames(Leitzaran4_post2)<-gsub("\\[|\\]", "_", colnames(Leitzaran4_post2))
colnames(Harpea7_post2)<-gsub("\\[|\\]", "_", colnames(Harpea7_post2))
colnames(Harpea5_post2)<-gsub("\\[|\\]", "_", colnames(Harpea5_post2))
colnames(Goizueta6_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta6_post2))
colnames(Goizueta7_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta7_post2))
colnames(Leitzaran7_post2)<-gsub("\\[|\\]", "_", colnames(Leitzaran7_post2))
colnames(Leitzaran5_post2)<-gsub("\\[|\\]", "_", colnames(Leitzaran5_post2))
colnames(Goizueta2_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta2_post2))
colnames(Erlan8_post2)<-gsub("\\[|\\]", "_", colnames(Erlan8_post2))
colnames(Goizueta5_post2)<-gsub("\\[|\\]", "_", colnames(Goizueta5_post2))
colnames(Harpea1_post2)<-gsub("\\[|\\]", "_", colnames(Harpea1_post2))
colnames(Harpea2_post2)<-gsub("\\[|\\]", "_", colnames(Harpea2_post2))
colnames(Harpea3_post2)<-gsub("\\[|\\]", "_", colnames(Harpea3_post2))
```

```{r data_subset, include=FALSE, eval=FALSE}
Harpea1_acclimatacion_subset<-subset(Harpea1_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta5_acclimatacion_subset<-subset(Goizueta5_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan8_acclimatacion_subset<-subset(Erlan8_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran7_acclimatacion_subset<-subset(Leitzaran7_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea5_acclimatacion_subset<-subset(Harpea5_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta7_acclimatacion_subset<-subset(Goizueta7_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran3_acclimatacion_subset<-subset(Leitzaran3_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan3_acclimatacion_subset<-subset(Erlan3_acclimatacion, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta1_post1_subset<-subset(Goizueta1_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran7_post1_subset<-subset(Leitzaran7_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan7_post1_subset<-subset(Erlan7_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran6_post1_subset<-subset(Leitzaran6_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta3_post1_subset<-subset(Goizueta3_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea1_post1_subset<-subset(Harpea1_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan5_post1_subset<-subset(Erlan5_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta5_post1_subset<-subset(Goizueta5_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan4_post1_subset<-subset(Erlan4_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea8_post1_subset<-subset(Harpea8_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta8_post1_subset<-subset(Goizueta8_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan3_post1_subset<-subset(Erlan3_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan2_post1_subset<-subset(Erlan2_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea6_post1_subset<-subset(Harpea6_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran3_post1_subset<-subset(Leitzaran3_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran4_post1_subset<-subset(Leitzaran4_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea3_post1_subset<-subset(Harpea3_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta2_post1_subset<-subset(Goizueta2_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea2_post1_subset<-subset(Harpea2_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta9_post1_subset<-subset(Goizueta9_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran5_post1_subset<-subset(Leitzaran5_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan8_post1_subset<-subset(Erlan8_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan6_post1_subset<-subset(Erlan6_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta3_post1_subset<-subset(Goizueta3_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta4_post1_subset<-subset(Goizueta4_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran2_post1_subset<-subset(Leitzaran2_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran1_post1_subset<-subset(Leitzaran1_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea5_post1_subset<-subset(Harpea5_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta7_post1_subset<-subset(Goizueta7_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta6_post1_subset<-subset(Goizueta6_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea7_post1_subset<-subset(Harpea7_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan1_post1_subset<-subset(Erlan1_post1, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta3_post2_subset<-subset(Goizueta3_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta9_post2_subset<-subset(Goizueta9_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta1_post2_subset<-subset(Goizueta1_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan6_post2_subset<-subset(Erlan6_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran6_post2_subset<-subset(Leitzaran6_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan5_post2_subset<-subset(Erlan5_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan7_post2_subset<-subset(Erlan7_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran3_post2_subset<-subset(Leitzaran3_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan3_post2_subset<-subset(Erlan3_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan2_post2_subset<-subset(Erlan2_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan1_post2_subset<-subset(Erlan1_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan4_post2_subset<-subset(Erlan4_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta8_post2_subset<-subset(Goizueta8_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea8_post2_subset<-subset(Harpea8_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran1_post2_subset<-subset(Leitzaran1_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea6_post2_subset<-subset(Harpea6_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran2_post2_subset<-subset(Leitzaran2_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta4_post2_subset<-subset(Goizueta4_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran4_post2_subset<-subset(Leitzaran4_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea7_post2_subset<-subset(Harpea7_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea5_post2_subset<-subset(Harpea5_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta6_post2_subset<-subset(Goizueta6_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta7_post2_subset<-subset(Goizueta7_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran7_post2_subset<-subset(Leitzaran7_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran5_post2_subset<-subset(Leitzaran5_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta2_post2_subset<-subset(Goizueta2_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan8_post2_subset<-subset(Erlan8_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta5_post2_subset<-subset(Goizueta5_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea1_post2_subset<-subset(Harpea1_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea2_post2_subset<-subset(Harpea2_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea3_post2_subset<-subset(Harpea3_post2, select=c("Time__A_Ch.1_Main_","Oxygen_(%O2)__A_Ch.1_Main_"))
```

```{r time_fix, include=FALSE, eval=FALSE}
Harpea1_acclimatacion_subset<-Harpea1_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta5_acclimatacion_subset<-Goizueta5_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan8_acclimatacion_subset<-Erlan8_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran7_acclimatacion_subset<-Leitzaran7_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea5_acclimatacion_subset<-Harpea5_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta7_acclimatacion_subset<-Goizueta7_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran3_acclimatacion_subset<-Leitzaran3_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan3_acclimatacion_subset<-Erlan3_acclimatacion_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta1_post1_subset<-Goizueta1_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran7_post1_subset<-Leitzaran7_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan7_post1_subset<-Erlan7_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran6_post1_subset<-Leitzaran6_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta3_post1_subset<-Goizueta3_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea1_post1_subset<-Harpea1_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan5_post1_subset<-Erlan5_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta5_post1_subset<-Goizueta5_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan4_post1_subset<-Erlan4_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea8_post1_subset<-Harpea8_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta8_post1_subset<-Goizueta8_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan3_post1_subset<-Erlan3_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan2_post1_subset<-Erlan2_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea6_post1_subset<-Harpea6_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran3_post1_subset<-Leitzaran3_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran4_post1_subset<-Leitzaran4_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea3_post1_subset<-Harpea3_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta2_post1_subset<-Goizueta2_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea2_post1_subset<-Harpea2_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta9_post1_subset<-Goizueta9_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran5_post1_subset<-Leitzaran5_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan8_post1_subset<-Erlan8_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan6_post1_subset<-Erlan6_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta3_post1_subset<-Goizueta3_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta4_post1_subset<-Goizueta4_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran2_post1_subset<-Leitzaran2_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran1_post1_subset<-Leitzaran1_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea5_post1_subset<-Harpea5_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta7_post1_subset<-Goizueta7_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta6_post1_subset<-Goizueta6_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea7_post1_subset<-Harpea7_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan1_post1_subset<-Erlan1_post1_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta3_post2_subset<-Goizueta3_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta9_post2_subset<-Goizueta9_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta1_post2_subset<-Goizueta1_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan6_post2_subset<-Erlan6_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran6_post2_subset<-Leitzaran6_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan5_post2_subset<-Erlan5_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan7_post2_subset<-Erlan7_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran3_post2_subset<-Leitzaran3_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan3_post2_subset<-Erlan3_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan2_post2_subset<-Erlan2_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan1_post2_subset<-Erlan1_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan4_post2_subset<-Erlan4_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta8_post2_subset<-Goizueta8_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea8_post2_subset<-Harpea8_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran1_post2_subset<-Leitzaran1_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea6_post2_subset<-Harpea6_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran2_post2_subset<-Leitzaran2_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta4_post2_subset<-Goizueta4_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran4_post2_subset<-Leitzaran4_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea7_post2_subset<-Harpea7_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea5_post2_subset<-Harpea5_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta6_post2_subset<-Goizueta6_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta7_post2_subset<-Goizueta7_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran7_post2_subset<-Leitzaran7_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Leitzaran5_post2_subset<-Leitzaran5_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta2_post2_subset<-Goizueta2_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Erlan8_post2_subset<-Erlan8_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Goizueta5_post2_subset<-Goizueta5_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea1_post2_subset<-Harpea1_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea2_post2_subset<-Harpea2_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
Harpea3_post2_subset<-Harpea3_post2_subset %>%  mutate(Time = as.numeric(hms::as_hms(Time__A_Ch.1_Main_)))
```

```{r data_subset_1, include=FALSE, eval=FALSE}
Harpea1_acclimatacion_subset<-subset(Harpea1_acclimatacion_subset, select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta5_acclimatacion_subset<-subset(Goizueta5_acclimatacion_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan8_acclimatacion_subset<-subset(Erlan8_acclimatacion_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran7_acclimatacion_subset<-subset(Leitzaran7_acclimatacion_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea5_acclimatacion_subset<-subset(Harpea5_acclimatacion_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta7_acclimatacion_subset<-subset(Goizueta7_acclimatacion_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran3_acclimatacion_subset<-subset(Leitzaran3_acclimatacion_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan3_acclimatacion_subset<-subset(Erlan3_acclimatacion_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta1_post1_subset<-subset(Goizueta1_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran7_post1_subset<-subset(Leitzaran7_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan7_post1_subset<-subset(Erlan7_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran6_post1_subset<-subset(Leitzaran6_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta3_post1_subset<-subset(Goizueta3_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea1_post1_subset<-subset(Harpea1_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan5_post1_subset<-subset(Erlan5_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta5_post1_subset<-subset(Goizueta5_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan4_post1_subset<-subset(Erlan4_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea8_post1_subset<-subset(Harpea8_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta8_post1_subset<-subset(Goizueta8_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan3_post1_subset<-subset(Erlan3_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan2_post1_subset<-subset(Erlan2_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea6_post1_subset<-subset(Harpea6_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran3_post1_subset<-subset(Leitzaran3_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran4_post1_subset<-subset(Leitzaran4_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea3_post1_subset<-subset(Harpea3_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta2_post1_subset<-subset(Goizueta2_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea2_post1_subset<-subset(Harpea2_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta9_post1_subset<-subset(Goizueta9_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran5_post1_subset<-subset(Leitzaran5_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan8_post1_subset<-subset(Erlan8_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan6_post1_subset<-subset(Erlan6_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta3_post1_subset<-subset(Goizueta3_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta4_post1_subset<-subset(Goizueta4_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran2_post1_subset<-subset(Leitzaran2_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran1_post1_subset<-subset(Leitzaran1_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea5_post1_subset<-subset(Harpea5_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta7_post1_subset<-subset(Goizueta7_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta6_post1_subset<-subset(Goizueta6_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea7_post1_subset<-subset(Harpea7_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan1_post1_subset<-subset(Erlan1_post1_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta3_post2_subset<-subset(Goizueta3_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta9_post2_subset<-subset(Goizueta9_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta1_post2_subset<-subset(Goizueta1_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan6_post2_subset<-subset(Erlan6_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran6_post2_subset<-subset(Leitzaran6_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan5_post2_subset<-subset(Erlan5_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan7_post2_subset<-subset(Erlan7_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran3_post2_subset<-subset(Leitzaran3_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan3_post2_subset<-subset(Erlan3_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan2_post2_subset<-subset(Erlan2_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan1_post2_subset<-subset(Erlan1_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan4_post2_subset<-subset(Erlan4_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta8_post2_subset<-subset(Goizueta8_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea8_post2_subset<-subset(Harpea8_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran1_post2_subset<-subset(Leitzaran1_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea6_post2_subset<-subset(Harpea6_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran2_post2_subset<-subset(Leitzaran2_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta4_post2_subset<-subset(Goizueta4_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran4_post2_subset<-subset(Leitzaran4_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea7_post2_subset<-subset(Harpea7_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea5_post2_subset<-subset(Harpea5_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta6_post2_subset<-subset(Goizueta6_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta7_post2_subset<-subset(Goizueta7_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran7_post2_subset<-subset(Leitzaran7_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Leitzaran5_post2_subset<-subset(Leitzaran5_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta2_post2_subset<-subset(Goizueta2_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Erlan8_post2_subset<-subset(Erlan8_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Goizueta5_post2_subset<-subset(Goizueta5_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea1_post2_subset<-subset(Harpea1_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea2_post2_subset<-subset(Harpea2_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
Harpea3_post2_subset<-subset(Harpea3_post2_subset,select=c("Time","Oxygen_(%O2)__A_Ch.1_Main_"))
```

```{r calc_rate, include=FALSE, eval=FALSE}
Harpea1_acclimatacion_rate<-calc_rate(Harpea1_acclimatacion_subset, from = 35400, to = 36484, by = "Time")
Goizueta5_acclimatacion_rate<-calc_rate(Goizueta5_acclimatacion_subset, from = 37000, to = 37935, by = "Time")
Erlan8_acclimatacion_rate<-calc_rate(Erlan8_acclimatacion_subset)
Leitzaran7_acclimatacion_rate<-calc_rate(Leitzaran7_acclimatacion_subset)
Harpea5_acclimatacion_rate<-calc_rate(Harpea5_acclimatacion_subset, from = 41654, to = 42700, by = "Time")
Goizueta7_acclimatacion_rate<-calc_rate(Goizueta7_acclimatacion_subset, from = 43424, to = 43885, by = "Time")
Leitzaran3_acclimatacion_rate<-calc_rate(Leitzaran3_acclimatacion_subset)
Erlan3_acclimatacion_rate<-calc_rate(Erlan3_acclimatacion_subset, from = 46232, to = 47194, by = "Time")
Goizueta1_post1_rate<-calc_rate(Goizueta1_post1_subset)
Leitzaran7_post1_rate<-calc_rate(Leitzaran7_post1_subset, from = 36801, to = 37564, by = "Time")
Erlan7_post1_rate<-calc_rate(Erlan7_post1_subset, from = 38005, to = 38803, by = "Time")
Leitzaran6_post1_rate<-calc_rate(Leitzaran6_post1_subset, from = 39200, to = 39999, by = "Time")
Goizueta3_post1_rate<-calc_rate(Goizueta3_post1_subset, from = 45045, to = 45981, by = "Time")
Harpea1_post1_rate<-calc_rate(Harpea1_post1_subset, from = 41800, to = 42629, by = "Time")
Erlan5_post1_rate<-calc_rate(Erlan5_post1_subset, from = 42938, to = 43876, by = "Time")
Goizueta5_post1_rate<-calc_rate(Goizueta5_post1_subset, from = 44192, to = 44798, by = "Time")
Erlan4_post1_rate<-calc_rate(Erlan4_post1_subset, from = 45546, to = 46146, by = "Time")
Harpea8_post1_rate<-calc_rate(Harpea8_post1_subset, from = 47361, to = 48090, by = "Time")
Goizueta8_post1_rate<-calc_rate(Goizueta8_post1_subset, from = 48385, to = 48998, by = "Time")
Erlan3_post1_rate<-calc_rate(Erlan3_post1_subset, from = 49515, to = 50438, by = "Time")
Erlan2_post1_rate<-calc_rate(Erlan2_post1_subset, from = 50793, to = 51717, by = "Time")
Harpea6_post1_rate<-calc_rate(Harpea6_post1_subset, from = 52013, to = 52960, by = "Time")
Leitzaran3_post1_rate<-calc_rate(Leitzaran3_post1_subset, from = 53228, to = 54166, by = "Time")
Leitzaran4_post1_rate<-calc_rate(Leitzaran4_post1_subset)
Harpea3_post1_rate<-calc_rate(Harpea3_post1_subset, from = 35058, to = 35964, by = "Time")
Goizueta2_post1_rate<-calc_rate(Goizueta2_post1_subset, from = 36635, to = 37577, by = "Time")
Harpea2_post1_rate<-calc_rate(Harpea2_post1_subset, from = 38116, to = 39183, by = "Time")
Goizueta9_post1_rate<-calc_rate(Goizueta9_post1_subset, from = 39516, to = 40491, by = "Time")
Leitzaran5_post1_rate<-calc_rate(Leitzaran5_post1_subset, from = 41333, to = 41771, by = "Time")
#Erlan8_post1_rate<-calc_rate(Erlan8_post1_subset)error measurement
Erlan6_post1_rate<-calc_rate(Erlan6_post1_subset, from = 43846, to = 44467, by = "Time")
Goizueta3_post1_rate<-calc_rate(Goizueta3_post1_subset, from = 45045, to = 45669, by = "Time")
Goizueta4_post1_rate<-calc_rate(Goizueta4_post1_subset, from = 46532, to = 47134, by = "Time")
Leitzaran2_post1_rate<-calc_rate(Leitzaran2_post1_subset, from = 47757, to = 48369, by = "Time")
Leitzaran1_post1_rate<-calc_rate(Leitzaran1_post1_subset, from = 49214, to = 49575, by = "Time")
Harpea5_post1_rate<-calc_rate(Harpea5_post1_subset, from = 50570, to = 51043, by = "Time")
Goizueta7_post1_rate<-calc_rate(Goizueta7_post1_subset, from = 51745, to = 52358, by = "Time")
Goizueta6_post1_rate<-calc_rate(Goizueta6_post1_subset, from = 52967, to = 53584, by = "Time")
Harpea7_post1_rate<-calc_rate(Harpea7_post1_subset, from = 54220, to = 54812, by = "Time")
Erlan1_post1_rate<-calc_rate(Erlan1_post1_subset, from = 55359, to = 55963, by = "Time")
#Goizueta3_post2_rate<-calc_rate(Goizueta3_post2_subset)error measurement
Goizueta9_post2_rate<-calc_rate(Goizueta9_post2_subset, from = 36329, to = 37272, by = "Time")
Goizueta1_post2_rate<-calc_rate(Goizueta1_post2_subset, from = 37700, to = 38619, by = "Time")
Erlan6_post2_rate<-calc_rate(Erlan6_post2_subset, from = 39019, to = 40079, by = "Time")
Leitzaran6_post2_rate<-calc_rate(Leitzaran6_post2_subset, from = 40482, to = 41425, by = "Time")
Erlan5_post2_rate<-calc_rate(Erlan5_post2_subset)
Erlan7_post2_rate<-calc_rate(Erlan7_post2_subset, from = 43306, to = 44256, by = "Time")
Leitzaran3_post2_rate<-calc_rate(Leitzaran3_post2_subset)
Erlan3_post2_rate<-calc_rate(Erlan3_post2_subset, from = 46301, to = 47203, by = "Time")
Erlan2_post2_rate<-calc_rate(Erlan2_post2_subset, from = 47627, to = 48565, by = "Time")
Erlan1_post2_rate<-calc_rate(Erlan1_post2_subset, from = 48973, to = 49910, by = "Time")
Erlan4_post2_rate<-calc_rate(Erlan4_post2_subset)
Goizueta8_post2_rate<-calc_rate(Goizueta8_post2_subset)
Harpea8_post2_rate<-calc_rate(Harpea8_post2_subset, from = 53243, to = 54145, by = "Time")
Leitzaran1_post2_rate<-calc_rate(Leitzaran1_post2_subset)
Harpea6_post2_rate<-calc_rate(Harpea6_post2_subset, from = 34497, to = 35400, by = "Time")
Leitzaran2_post2_rate<-calc_rate(Leitzaran2_post2_subset)
Goizueta4_post2_rate<-calc_rate(Goizueta4_post2_subset, from = 38310, to = 38917, by = "Time")
Leitzaran4_post2_rate<-calc_rate(Leitzaran4_post2_subset, from = 39669, to = 40297, by = "Time")
Harpea7_post2_rate<-calc_rate(Harpea7_post2_subset, from = 40901, to = 41527, by = "Time")
#Harpea5_post2_rate<-calc_rate(Harpea5_post2_subset) error measurement
Goizueta6_post2_rate<-calc_rate(Goizueta6_post2_subset, from = 44003, to = 44586, by = "Time")
Goizueta7_post2_rate<-calc_rate(Goizueta7_post2_subset, from = 45455, to = 46057, by = "Time")
#Leitzaran7_post2_rate<-calc_rate(Leitzaran7_post2_subset) error measurement
Leitzaran5_post2_rate<-calc_rate(Leitzaran5_post2_subset)
Goizueta2_post2_rate<-calc_rate(Goizueta2_post2_subset, from = 49620, to = 50227, by = "Time")
Erlan8_post2_rate<-calc_rate(Erlan8_post2_subset)
Goizueta5_post2_rate<-calc_rate(Goizueta5_post2_subset)
Harpea1_post2_rate<-calc_rate(Harpea1_post2_subset)
Harpea2_post2_rate<-calc_rate(Harpea2_post2_subset, from = 38314, to = 39212, by = "Time")
Harpea3_post2_rate<-calc_rate(Harpea3_post2_subset)
```

```{r calc_rate_1, comment=FALSE, message=FALSE, warning=FALSE, echo=FALSE, include=FALSE, eval=FALSE}
print(Harpea1_acclimatacion_rate)
print(Goizueta5_acclimatacion_rate)
print(Erlan8_acclimatacion_rate)
print(Leitzaran7_acclimatacion_rate)
print(Harpea5_acclimatacion_rate)
print(Goizueta7_acclimatacion_rate)
print(Leitzaran3_acclimatacion_rate)
print(Erlan3_acclimatacion_rate)
print(Goizueta1_post1_rate)
print(Leitzaran7_post1_rate)
print(Erlan7_post1_rate)
print(Leitzaran6_post1_rate)
print(Goizueta3_post1_rate)
print(Harpea1_post1_rate)
print(Erlan5_post1_rate)
print(Goizueta5_post1_rate)
print(Erlan4_post1_rate)
print(Harpea8_post1_rate)
print(Goizueta8_post1_rate)
print(Erlan3_post1_rate)
print(Erlan2_post1_rate)
print(Harpea6_post1_rate)
print(Leitzaran3_post1_rate)
print(Leitzaran4_post1_rate)
print(Harpea3_post1_rate)
print(Goizueta2_post1_rate)
print(Harpea2_post1_rate)
print(Goizueta9_post1_rate)
print(Leitzaran5_post1_rate)
#print(Erlan8_post1_rate)
print(Erlan6_post1_rate)
print(Goizueta3_post1_rate)
print(Goizueta4_post1_rate)
print(Leitzaran2_post1_rate)
print(Leitzaran1_post1_rate)
print(Harpea5_post1_rate)
print(Goizueta7_post1_rate)
print(Goizueta6_post1_rate)
print(Harpea7_post1_rate)
print(Erlan1_post1_rate)
#print(Goizueta3_post2_rate)
print(Goizueta9_post2_rate)
print(Goizueta1_post2_rate)
print(Erlan6_post2_rate)
print(Leitzaran6_post2_rate)
print(Erlan5_post2_rate)
print(Erlan7_post2_rate)
print(Leitzaran3_post2_rate)
print(Erlan3_post2_rate)
print(Erlan2_post2_rate)
print(Erlan1_post2_rate)
print(Erlan4_post2_rate)
print(Goizueta8_post2_rate)
print(Harpea8_post2_rate)
print(Leitzaran1_post2_rate)
print(Harpea6_post2_rate)
print(Leitzaran2_post2_rate)
print(Goizueta4_post2_rate)
print(Leitzaran4_post2_rate)
print(Harpea7_post2_rate)
#print(Harpea5_post2_rate)
print(Goizueta6_post2_rate)
print(Goizueta7_post2_rate)
#print(Leitzaran7_post2_rate)
print(Leitzaran5_post2_rate)
print(Goizueta2_post2_rate)
print(Erlan8_post2_rate)
print(Goizueta5_post2_rate)
print(Harpea1_post2_rate)
print(Harpea2_post2_rate)
print(Harpea3_post2_rate)
```

```{r data_load_r}
load("data/data.Rdata")
```


```{r calc_rate_plot, comment=FALSE, message=FALSE, warning=FALSE,results='hide', fig.height=6, fig.width=10, fig.fullwidth=TRUE}
plot(Harpea1_acclimatacion_rate)
plot(Goizueta5_acclimatacion_rate)
plot(Erlan8_acclimatacion_rate)
plot(Leitzaran7_acclimatacion_rate)
plot(Harpea5_acclimatacion_rate)
plot(Goizueta7_acclimatacion_rate)
plot(Leitzaran3_acclimatacion_rate)
plot(Erlan3_acclimatacion_rate)
plot(Goizueta1_post1_rate)
plot(Leitzaran7_post1_rate)
plot(Erlan7_post1_rate)
plot(Leitzaran6_post1_rate)
plot(Goizueta3_post1_rate)
plot(Harpea1_post1_rate)
plot(Erlan5_post1_rate)
plot(Goizueta5_post1_rate)
plot(Erlan4_post1_rate)
plot(Harpea8_post1_rate)
plot(Goizueta8_post1_rate)
plot(Erlan3_post1_rate)
plot(Erlan2_post1_rate)
plot(Harpea6_post1_rate)
plot(Leitzaran3_post1_rate)
plot(Leitzaran4_post1_rate)
plot(Harpea3_post1_rate)
plot(Goizueta2_post1_rate)
plot(Harpea2_post1_rate)
plot(Goizueta9_post1_rate)
plot(Leitzaran5_post1_rate)
#plot(Erlan8_post1_rate)
plot(Erlan6_post1_rate)
plot(Goizueta3_post1_rate)
plot(Goizueta4_post1_rate)
plot(Leitzaran2_post1_rate)
plot(Leitzaran1_post1_rate)
plot(Harpea5_post1_rate)
plot(Goizueta7_post1_rate)
plot(Goizueta6_post1_rate)
plot(Harpea7_post1_rate)
plot(Erlan1_post1_rate)
#plot(Goizueta3_post2_rate)
plot(Goizueta9_post2_rate)
plot(Goizueta1_post2_rate)
plot(Erlan6_post2_rate)
plot(Leitzaran6_post2_rate)
plot(Erlan5_post2_rate)
plot(Erlan7_post2_rate)
plot(Leitzaran3_post2_rate)
plot(Erlan3_post2_rate)
plot(Erlan2_post2_rate)
plot(Erlan1_post2_rate)
plot(Erlan4_post2_rate)
plot(Goizueta8_post2_rate)
plot(Harpea8_post2_rate)
plot(Leitzaran1_post2_rate)
plot(Harpea6_post2_rate)
plot(Leitzaran2_post2_rate)
plot(Goizueta4_post2_rate)
plot(Leitzaran4_post2_rate)
plot(Harpea7_post2_rate)
#plot(Harpea5_post2_rate)
plot(Goizueta6_post2_rate)
plot(Goizueta7_post2_rate)
#plot(Leitzaran7_post2_rate)
plot(Leitzaran5_post2_rate)
plot(Goizueta2_post2_rate)
plot(Erlan8_post2_rate)
plot(Goizueta5_post2_rate)
plot(Harpea1_post2_rate)
plot(Harpea2_post2_rate)
plot(Harpea3_post2_rate)
```

# Import dataframe

```{r data_import}
calotriton_resp1 <- read_excel("calotriton_resp1_metadata.xlsx")

calotriton_resp1$individual<-as.factor(calotriton_resp1$individual)
calotriton_resp1$population<-as.factor(calotriton_resp1$population)
calotriton_resp1$time_point<-as.factor(calotriton_resp1$time_point)
calotriton_resp1$elevation<-as.factor(calotriton_resp1$elevation)
calotriton_resp1$temperature<-as.factor(calotriton_resp1$temperature)
```

# Weight distribution among groups

```{r plot_weight}
calotriton_resp1 %>%
  filter(time_point=="0")%>%
  ggplot(aes(x = population, y = weight, color=temperature, shape=temperature, alpha=0.2)) +
    geom_boxplot()+
    geom_jitter()+
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))+
    stat_compare_means(size=3,vjust = 0.8, hjust=1 )+
    theme(legend.position="right")+
    labs(x = "Population", y= "Weight (g)")
```

```{r plot_weight_3}
weight_subset<-calotriton_resp1 %>%
  filter(time_point=="0")

#Overall
weight_subset$weight %>% mean()
weight_subset$weight %>% sd()

#In high elevation newts
weight_subset_high<-weight_subset %>% 
  filter(elevation=="High")

weight_subset_high$weight %>% mean()
weight_subset_high$weight %>% sd()

#In low elevation newts
weight_subset_low<-weight_subset %>% 
  filter(elevation=="Low")

weight_subset_low$weight %>% mean()
weight_subset_low$weight %>% sd()
```

## Metabolic scaling at the acclimation time-point

```{r plot_weight_1}

ggplot(weight_subset, aes(weight,o2, color=population, shape=temperature)) + 
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x)+
    stat_poly_eq()+
    labs(x = "Weight (g)", y= "O2 consumption (ml/s)")
```

### High elevation newts
```{r cor_weight_1}

ggplot(weight_subset_high, aes(weight ,o2, shape=temperature)) + 
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x)+
    stat_poly_eq()+
    labs(x = "Weight (g)", y= "O2 consumption (ml/s)")
```

### Low elevation newts
```{r cor_weight_2}
ggplot(weight_subset_low, aes(weight ,o2, shape=temperature)) + 
  geom_point() +
  geom_smooth(method = lm, formula = y ~ x)+
    stat_poly_eq()+
    labs(x = "Weight (g)", y= "O2 consumption (ml/s)")
```

## Metabolic scaling at each group and time-point

```{r plot_weight_2}
ggplot(calotriton_resp1, aes(weight ,o2)) + 
  geom_point() +
  facet_grid(temperature~ factor(population)+time_point)+
  geom_smooth(method = lm, formula = y ~ x)+
    stat_poly_eq()+
    labs(x = "Weight (g)", y= "O2 consumption (ml/s)")
```

#Acclimation oxygen consumption per population

```{r plot}
calotriton_resp1 %>%
  filter(time_point=="0")%>%
  ggplot(aes(x = population, y = o2_normalized, color=temperature, shape=temperature, alpha=0.2)) +
    geom_boxplot()+
    geom_jitter() +
    #geom_text(aes(label = individual), hjust = 0, nudge_x = 0.05) +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))+
    stat_compare_means(size=3,vjust = 0.8, hjust=1 )+
    theme(legend.position="right")+
    labs(x = "Population", y= "Normalized o2 consumption (ml/s/g)")
```

#Acclimation oxygen consumption per elevation

```{r plot_1}
calotriton_resp1 %>%
  filter(time_point=="0")%>%
  ggplot(aes(x = elevation, y = o2_normalized, shape=temperature, alpha=0.2)) +
    geom_boxplot()+
    geom_jitter() +
    #geom_text(aes(label = individual), hjust = 0, nudge_x = 0.05) +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))+
    stat_compare_means(size=3,vjust = 0.8, hjust=1 )+
    theme(legend.position="right")+
    labs(x = "Population", y= "Normalized o2 consumption (ml/s/g)")
```

#Acclimation oxygen consumption per temperature

```{r plot_5}
calotriton_resp1 %>%
  filter(time_point=="0")%>%
  ggplot(aes(x = temperature, y = o2_normalized, colour=population, alpha=0.2)) +
    geom_boxplot()+
    geom_jitter() +
    #geom_text(aes(label = individual), hjust = 0, nudge_x = 0.05) +
    theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1))+
    stat_compare_means(size=3,vjust = 0.8, hjust=1 )+
    theme(legend.position="right")+
    labs(x = "Population", y= "Normalized o2 consumption (ml/s/g)")
```

# Time-point oxygen consumption

```{r plot_6}
calotriton_resp1 %>%
  filter(time_point!="0") %>%
  ggplot(aes(x = time_point, y = o2_normalized, color=time_point, alpha=0.2)) +
    geom_boxplot()+
    geom_jitter() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    facet_wrap(~ factor(temperature)+elevation)+
    stat_compare_means(size=3)+
    theme(legend.position="right")+
    labs(x = "Time_point", y= "Normalized o2 consumption (ml/s/g)")
```

```{r plot_3}
calotriton_resp1 %>%
  filter(time_point!="0") %>%
  ggplot(aes(x = time_point, y = o2_normalized, color=time_point, alpha=0.2)) +
    geom_boxplot()+
    geom_jitter() +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))+
    facet_grid(temperature~factor(elevation)+population)+
    stat_compare_means(size=3)+
    theme(legend.position="right")+
    labs(x = "Time_point", y= "Normalized o2 consumption (ml/s/g)")
```

# Time-point oxygen consumption, linking individuals

```{r plot_2}
calotriton_resp1 %>%
  filter(time_point!="0") %>%
  ggplot(aes(y = o2_normalized, x = interaction(time_point, individual), color = time_point, fill = time_point)) +
  geom_point(position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.8), alpha = 0.5) +
  facet_grid(temperature~factor(elevation)+population, scale="free") +
  geom_line(aes(group=individual)) +
  theme_minimal()+
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, size=0))+
  labs(x = "Time-point", y = "Normalized o2 consumption (ml/s/g)", color = "Time-point", fill = "Time-point")
```

# Raw data modelling (LMM)

```{r model}
#exclude the acclimation time-point
calotriton_resp1_subset<-calotriton_resp1 %>%
  filter(time_point!="0")


#Create linear model formula
formula <- formula(o2_normalized ~ time_point*temperature*population+(1|individual))

#Fit the linear model
model <- lmer(formula, data = calotriton_resp1_subset)

#Print the model summary
summary(model)
MuMIn::r.squaredGLMM(model)

```

## Raw data modelling (LM) without random effect

```{r model_1}
#Create linear model formula
formula1 <- formula(o2_normalized ~ time_point*temperature*population) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model1 <- lm(formula1, data = calotriton_resp1_subset)

#Print the model summary
summary(model1)
```

# Raw data modelling (LMM) without interaction

```{r model_2}
#Create linear model formula
formula3 <- formula(o2_normalized ~ time_point*temperature+population+(1|individual))

#Fit the linear model
model3 <- lmer(formula3, data = calotriton_resp1_subset)

#Print the model summary
summary(model3)
MuMIn::r.squaredGLMM(model3)
```

## Raw data modelling (LM) without random effect and interaction

```{r model_3}
#Create linear model formula
formula2 <- formula(o2_normalized ~ time_point*temperature+population) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model2 <- lm(formula2, data = calotriton_resp1_subset)

#Print the model summary
summary(model2)
```

## Raw data modelling (LM) without random effect and using elevation and not population

```{r model_4}
#Create linear model formula
formula4 <- formula(o2_normalized ~ time_point*temperature+elevation) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model4 <- lm(formula4, data = calotriton_resp1_subset)

#Print the model summary
summary(model4)
```


## Raw data modelling (LM) without random effect and using elevation as interaction

```{r model_5}
#Create linear model formula
formula5 <- formula(o2_normalized ~ time_point*temperature*elevation) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model5 <- lm(formula5, data = calotriton_resp1_subset)

#Print the model summary
summary(model5)
```

## Raw data modelling (LM) without random effect and using elevation as interaction with temperature

```{r model_6}
#Create linear model formula
formula6 <- formula(o2_normalized ~ time_point+temperature*elevation) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model6 <- lm(formula6, data = calotriton_resp1_subset)

#Print the model summary
summary(model6)
```

## Raw data modelling (LM) without random effect and using elevation as interaction with time-point

```{r model_7}
#Create linear model formula
formula7 <- formula(o2_normalized ~ time_point*elevation+temperature) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model7 <- lm(formula7, data = calotriton_resp1_subset)

#Print the model summary
summary(model7)
```

## Raw data modelling (LM) without random effect and population as interaction with temperature

```{r model_8}
#Create linear model formula
formula8 <- formula(o2_normalized ~ time_point+temperature*population) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model8 <- lm(formula8, data = calotriton_resp1_subset)

#Print the model summary
summary(model8)
```

## Raw data modelling (LM) without random effect and population as interaction with time-point

```{r model_9}
#Create linear model formula
formula9 <- formula(o2_normalized ~ time_point*population+temperature) #QC_normalized=o2 consumption normalized (ml/s/g)

#Fit the linear model
model9 <- lm(formula9, data = calotriton_resp1_subset)

#Print the model summary
summary(model9)
```
